\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english, icelandic]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{gensymb}
\usepackage{parskip}
\usepackage{mathtools}
\usepackage{xfrac}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{verbatim}
\usepackage{multicol}
\parskip 0pt

\DeclareMathOperator{\lcm}{lcm}
\DeclareMathOperator{\diam}{diam}
\DeclareMathOperator{\dist}{dist}
\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\Inn}{Inn}
\DeclareMathOperator{\Ker}{Ker}
\DeclareMathOperator{\trace}{trace}
\DeclareMathOperator{\fix}{fix}
\newcommand\floor[1]{\left\lfloor#1\right\rfloor}
\newcommand\ceil[1]{\left\lceil#1\right\rceil}
\newcommand\abs[1]{\left|#1\right|}
\newcommand\p[1]{\left(#1\right)}
\newcommand\sqp[1]{\left[#1\right]}
\newcommand\cp[1]{\left\{#1\right\}}
\renewcommand\qedsymbol{$\blacksquare$}
\renewcommand\Im{\operatorname{Im}}
\renewcommand\Re{\operatorname{Re}}

\pagenumbering{gobble}

\graphicspath{{myndir/}}

\begin{document}

\begin{titlepage}
	\centering
	{\scshape\LARGE University of Iceland \par}
	\vspace{1cm}
	{\scshape\Large HBV401G Software Development \par}
	\vspace{1.5cm}
	{\huge\bfseries User stories \par}
	\vspace{2cm}
	{\Large\itshape Atli Fannar Franklín \\ Ólafur Einar Ómarsson \\ Jón Freyr Bjarnason \\ 8H\par}
	\vfill
	Teacher: \par
	Matthias Book \par 

	\vfill

	{\large \today\par}
\end{titlepage}

\section*{Team members:}

On this team there are three members: Atli Fannar Franklín (kt: 2612982609), Ólafur Einar Ómarsson (kt: 2009912739) and Jón Freyr Bjarnason (kt: 0509932649). The team number is 8H. Atli Fannar Franklín will be presenting next Wednesday.

\section*{User stories:}

\begin{itemize}

\item As a visitor, I want to be able to order hotels based on distance from a given point so I can find hotels close to where I'll be spending my time.

\item As a visitor, I want to view pictures of the hotel and rooms to see if the room meets my expectations.

\item As a visitor, I want to be able to read what amenities are available in the room in order to determine if the room matches my needs.

\item As a visitor, I want to be able to sort rooms by size, price, and amenities, so I am able to pick a room that suits my needs.

\item As a visitor, I want to see which hotels are pet friendly, because I have allergies.

\item As a visitor, I want to see when the checkout time for the hotel is, so I can plan when to leave the room.

\item As a hotel manager, I want to be able to post a hotel and configure how many rooms are available and their respective prices, so I can give potential customers information about my hotel. 

\item As a hotel manager, I want to be able to charge travelers who have booked a room, so I can confirm the booking. 

\item As a hotel manager, I want to get payment information from customers when they book a room, so I have the ability to charge for late cancellation

\item As a hotel manager, I want to be able to respond to reviews and dispute false ones, since reviews are very important when travelers choose hotels.

\item As a trip planner, I want to have an interface to bundle together room offerings, so I can make bookings on the behalf of my customers.

\item As a tax inspector, I need access to the tax identification numbers of the hotels, to fullfill my legal responsibility to survey hotel service providers. 

\end{itemize}

\end{document}